Meeting the Challenges of Modeling Astrophysical Thermonuclear Explosions: \castro, \maestro, and the \amrex\ Astrophysics Suite

### 2017-10-24 astronum_2017/astronum-amrex.tex
marginpar about other castro works, if wanted

\castro\ has been applied to core-collapse
supernovae~\cite{castro-ccsne}, population III pair-instability
supernovae~\cite{castro-pairinstability}, and white dwarf mergers as a
model for SNe Ia~\cite{wdmergerI}.  Recent work has focused on
improving energy conservation with gravitational and rotational
sources, and new integration methods that more accurately couple hydro
and reactions.  For \maestro\ simulations that evolve from the
subsonic regime to the sonic regime, we have demonstrated the ability
to restart the calculations in \castro\ to continue the evolution into
the sonic regime~\cite{scidac-petascale,malone:2014} (in this case,
for Chandra model SNe Ia).

>>>>

\castro\ has been applied to core-collapse
supernovae~\cite{castro-ccsne}, population III pair-instability
supernovae~\cite{castro-pairinstability}, and white dwarf mergers as a
model for SNe Ia~\cite{wdmergerI}. \MarginPar{There are others: Ma's
  Chandra model of SNe Ia; Lovegrove's shock breakout; Moll's WD
  merger; Moll's double det in subCh.} Recent work has focused on
improving energy conservation with gravitational and rotational
sources, and new integration methods that more accurately couple hydro
and reactions.  For \maestro\ simulations that evolve from the
subsonic regime to the sonic regime, we have demonstrated the ability
to restart the calculations in \castro\ to continue the evolution into
the sonic regime~\cite{scidac-petascale,malone:2014} (in this case,
for Chandra model SNe Ia).
